---
title: "Effects of Monetary Policy in Australia with Package **bsvars**"
author: 
  - name: "Type your name"
format:
  html:
    theme: cosmo
    toc: true

---

> **Task:** Adjust this **Quarto** template to perform your Bayesian Structural VAR model estimation and impolse response analysis of th monetary policy in Australia. 

# Install packages
```{r install}
#| eval: false
install.packages("devtools")
devtools::install_git("https://github.com/donotdespair/bsvars.git")
devtools::install_git("https://github.com/donotdespair/bsvarTVPs.git")
```


# Download the data

```{r data}
#| echo: true
#| message: false
#| warning: false
#| cache: true

# Gross domestic product (GDP); Chain volume
rgdp_dwnld      = readrba::read_rba(series_id = "GGDPCVGDP")
rgdp_tmp        = xts::xts(rgdp_dwnld$value, rgdp_dwnld$date, tclass = 'yearqtr')
drgdp           = na.omit(400 * diff(log(rgdp_tmp)))
drgdp           = xts::to.quarterly(drgdp, OHLC = FALSE)

# Consumer price index; All groups; Quarterly change (in per cent)
picpi_dwnld     = readrba::read_rba(series_id = "GCPIAGSAQP")
pi              = 4 * xts::xts(picpi_dwnld$value, picpi_dwnld$date, tclass = 'yearqtr')
pi              = xts::to.quarterly(pi, OHLC = FALSE)

# Interbank Overnight Cash Rate
cr_dwnld        = readrba::read_rba(series_id = "FIRMMCRID")   # Cash Rate Target
cr_tmp          = xts::xts(cr_dwnld$value, cr_dwnld$date)
cr              = xts::to.quarterly(cr_tmp, OHLC = FALSE)

# Real Trade-Weighted Index
rtwi_dwnld      = readrba::read_rba(series_id = "FRERTWI")
rtwi_tmp        = xts::xts(rtwi_dwnld$value, rtwi_dwnld$date, tclass = 'yearqtr')
rtwi            = 100 * na.omit(diff(log(rtwi_tmp)))
rtwi            = xts::to.quarterly(rtwi, OHLC = FALSE)

y               = na.omit(merge(drgdp, pi, cr, rtwi))
plot(y, legend.loc = "bottomright")
```

# Model Equations

\begin{align}
y_t &= \begin{bmatrix}\Delta rgdp_t & \pi_t & cr_t & \Delta rtwi_t\end{bmatrix}'\\
y_t &= A_1 y_{t-1} + \dots + A_9 y_{t-9} + \mu_0 + \epsilon_t\\
B \epsilon_t &= u_t\\
u_t | Y_{t-1} &\sim\mathcal{N}_N\left(\mathbf{0}_N, \mathbf{I}_N\right)
\end{align}

# Model Setup

```{r setup}
set.seed(123)
library(bsvars)

spec_bsvar      = specify_bsvar$new(
  as.matrix(y), 
  p = 5, 
  stationary = rep(TRUE, 4)
)

A_mle           = t(solve(
  tcrossprod(spec_bsvar$data_matrices$X), 
  tcrossprod(spec_bsvar$data_matrices$X, spec_bsvar$data_matrices$Y)
))
spec_bsvar$prior$A = A_mle
```

# Estimation

## Estimate the model

```{r estimation}
#| echo: true
#| message: false
#| warning: false
#| error: false
#| cache: true

spec_bsvar |> 
  estimate(S = 10000, show_progress = FALSE) |> 
  estimate(S = 20000, thin = 2) -> soe_bsvar
```

## Report MCMC convergence

```{r mcmc}
plot.ts(t(soe_bsvar$posterior$B[,1,]), main = "", col = "#9933FF", xlab = "s")
```

## Report the Posterior Moments

### Autoregressive parameters $A$
```{r meansA}
mean_A  = apply(soe_bsvar$posterior$A, 1:2, mean)
rownames(mean_A) = colnames(y)
knitr::kable(mean_A, caption = "Posterior estimates for autoregressive parameters", digits = 3)
```

### Structural parameters $B$
```{r meansB}
mean_B  = apply(soe_bsvar$posterior$B, 1:2, mean)
rownames(mean_B) = colnames(y)
knitr::kable(mean_B, caption = "Posterior estimates for structural parameters", digits = 3)
```

# Impulse Responses analysis

## Responses to the monetary policy shock
```{r irf}
ir            = compute_impulse_responses(soe_bsvar, horizon = 20)
# rescale the cash rate effects
ir[,3,,] = 0.25 * ir[,3,,] / mean(ir[3,3,1,])

for (n in 1:4) {
  bsvarTVPs::ribbon_plot(
    ir[n,3,,],
    main = paste("Response of",colnames(y)[n],"to the mps"),
    ylab = colnames(y)[n],
    xlab = "horizon [quarters]",
    bty  = "n",
  )
  abline(h = 0)
}

```

# Conclusion!

Thank you!